On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2019-02-04 docs/mvfits_paper/referee_reports_and_responses/Response_Ref1.txt

Response for Referee #1
---

1. (p. 1, L16-17) The referee makes a valid, though largely semantic point regarding the use of interpolating in the abstract as it related to GMVR and Runge's phenomenon. We kindly note that GMVR is an iterative regression method that works for equally spaced grids, and constructs rational functions (equivalently, sums of rational functions) that smoothly connect or interpolate data assuming a rational ansatz.

@@

10. (p. 2, L30) Thank you. We agree that Yang+ should be referenced here.

11. (p. 2, L39) Thank you. We have updated this section to avoid any confusion.

12. (In Eq.6) Thank you. We have clarified the notation.

13. (p. 2, L26-27) Thank you for mentioning the Stone-Weierstrass theorem. We do not wish to reference this theorem in place of the series expansion as the latter is more accessible to a physics audience. We note that our introduction to the discussion is generally applicable given some smooth function and an epsilon neighbourhood around a point. We intend primarily to motivate a general multinomial basis perspective of our algorithms from first principles. he text has been modified in an effort to clarify this intention.

@@

14. (Algs. 2 and 5 ...) Thank you. We have clarified that we refer to the set of all multinomial combinations of basis vectors up to a predefined maximum order.

15. (Algs. 2 and 5 ...) Thank you. We have corrected these lines to reference epsilons.

16. (p. 3, L60) The current description of \lambda_{bulk} seeks to communicate the presence of the constant term.

17. (p. 5, L3-4) We refer the reviewer to the introduction section here: https://en.wikipedia.org/wiki/Runge%27s_phenomenon. We have sought to clarify the text to minimise confusion.

@@

18. ( Eq. 20 ) We refer the referee to Eq 21

19. (Alg. 3, step 3) The algorithm as stated applies to multiple definitions of the representation error. We now accentuate this point by citing the L2 norm as a possible choice.

20. (Alg. 4, step 2) Via Eq. 15, n>=1 for alpha. Here, "implicitly" n plays no real role in the algorithm and therefore need not be stored and incremented.

21. (Alg. 4, step 4) Thank you. We have defined var to be the variance.

22. (Alg. 4, step 10) Thank you. Yes.

23. (p. 8, final line) We have clarified the text.

24. (Fig. 4) We have clarified the text.

25. Code: While we are appreciative of the referee's comments, we point out to the submitted draft only pertains to the GMVP and GMVR algorithms.

### 2019-02-04 docs/mvfits_paper/mvf.tex
Add minor changes to tex and res txt for response

This perspective reflects the empirical observation that the remnant spin of \bbh{} mergers smoothly connects regions of positive and negative spin relative to the direction of the initial oribital angular momentum \cite{Husa:2015iqa,London:2018gaq}.

@@

As with the \qnm{} frequencies, residuals are dominated by small scale oscillations with amplitudes that are fractions of a percent of the central values, and largely result from the model asatz.

>>>>

This perspective reflects the empirical observation that the remnant spin of \bbh{} mergers smoothly connects regions of positive and negative spin relative to the direction of the initial orbital angular momentum \cite{Husa:2015iqa,London:2018gaq}.

@@

As with the \qnm{} frequencies, residuals are dominated by small scale oscillations with amplitudes that are fractions of a percent of the central values, and largely result from the model ansatz.
